---
title: "DEdwards_Week6CaseStudy"
output:
  html_document: default
---

## Introduction

The growth of wireless networking has generated commercial and research interests in statistical methods to reliably track people and things inside stores, hospitals, warehouses, and factories. GPS' do not work reliably inside buildings, but with the proliferation of wireless LAN's, indoor positioning systems (IPS) can utilize WiFi signals detected from network access points to answer questions such as: where is a piece of equipment in a hospital? where am I? and who are my neighbors? Ideally, with minimal training, calibration, and equipment, these questions can be answered well in near real-time. To build an indoor positioning system requires a reference set of data where the signal strength between a hand-held device such as a cellular phone or laptop and fixed access points (routers) are measured at known locations throughout the building. With these training data, we can build a model for the location of a device as a function of the strength of the signals between the device and each access point. Then we use this model to predict the location of a new unknown device based on the detected signals for the device. In this chapter, we examine nearly one million measurements of signal strength recorded at 6 stationary WiFi access points  within a building at the University of Mannheim and develop a statistical IPS. (Nolan & Lang, 2015)

This case study has already been completed, the objective this report is to expand on the work that has already been completed in the book, Data Science in R: A Case Studies approach to Computational Reasoning and Problem Solving. In the original case study, one of the MAC addresses (00:0f:a3:39:dd:cd) were removed from the dataset and we will be looking at how adding the address back and removing another MAC address effects the prediction analysis. Also, in the original case study a simple average of nearest neighbors to predict location but for this study we will be using a weighted average based on the distance from test observations. 



**Load the Data**

```{r}
options(digits = 2)
set.seed(1906)
txt = readLines("http://www.rdatasciencecases.org/Data/offline.final.trace.txt")
```




```{r}
processLine = function(x)
{
  tokens = strsplit(x, "[;=,]")[[1]]
  
  if (length(tokens) == 10) 
    return(NULL)
 
  tmp = matrix(tokens[ - (1:10) ], , 4, byrow = TRUE)
  cbind(matrix(tokens[c(2, 4, 6:8, 10)], nrow(tmp), 6, 
               byrow = TRUE), tmp)
}
 
lines = txt[substr(txt, 1, 1) != "#"]
options(error = recover, warn = 1)
tmp = lapply(lines, processLine)
offline = as.data.frame(do.call("rbind", tmp), 
                        stringsAsFactors = FALSE)

dim(offline)

```

Assign variables

```{r}
names(offline) = c("time", "scanMac", "posX", "posY", "posZ", 
                   "orientation", "mac", "signal", 
                   "channel", "type")

numVars = c("time", "posX", "posY", "posZ", 
            "orientation", "signal")
offline[ numVars ] =  lapply(offline[ numVars ], as.numeric)
```


```{r}
offline = offline[ offline$type == "3", ]
offline = offline[ , "type" != names(offline) ]

```

Time format conversion

```{r}
offline$rawTime = offline$time
offline$time = offline$time/1000
class(offline$time) = c("POSIXt", "POSIXct")


```


Convert character variables to factor variables

```{r}
summary(sapply(offline[ , c("mac", "channel", "scanMac")],
                as.factor))
```

The value of scanMac is the MAC address of the mobile device, and since the altitude value posZ is 0 in the first layer

```{r}
offline = offline[ , !(names(offline) %in% c("scanMac", "posZ"))]
```

There are eight directions, and there are 203 direction values. 0, 45, ... , 315 (0 or near 360 are mapped to 0)

```{r}
roundOrientation = function(angles) {
  refs = seq(0, by = 45, length  = 9)
  q = sapply(angles, function(o) which.min(abs(o - refs)))
  c(refs[1:8], 0)[q]
}

offline$angle = roundOrientation(offline$orientation)
with(offline, boxplot(orientation~angle, 
                      xlab="nearest 45 degree angle",
                      yalb="orientation"))
```

There are 8 MAC addresses, 12 MAC addresses and 8 channels. 

Figure1
```{r}
c(length(unique(offline$mac)), length(unique(offline$channel)))

```

There are 8 MAC addresses, 12 MAC addresses and 8 channels. 

```{r}
subMacs = names(sort(table(offline$mac), decreasing = TRUE))[1:7]
offline = offline[ offline$mac %in% subMacs, ]
macChannel = with(offline, table(mac, channel))
apply(macChannel, 1, function(x) sum(x > 0))
```

```{r}
offline = offline[ , "channel" != names(offline)]
```

Exclude null values

```{r}
locDF = with(offline, 
             by(offline, list(posX, posY), function(x) x))
#length(locDF)
```

```{r}
sum(sapply(locDF, is.null))
```

```{r}
locDF = locDF[ !sapply(locDF, is.null) ]
length(locDF)
```

Observations recorded at each location

```{r}
locCounts = sapply(locDF, nrow)
locCounts = sapply(locDF, 
                   function(df) 
                     c(df[1, c("posX", "posY")], count = nrow(df)))
#class(locCounts)
```



```{r}
locCounts[ , 1:8]
```

Visualize your location

```{r}
locCounts = t(locCounts)
plot(locCounts, type = "n", xlab = "", ylab = "")
text(locCounts, labels = locCounts[,3], cex = .8, srt = 45)

```
Figure 2


Signal strength

Calculate summary values for 166 locations because each location is difficult to see

```{r}
offline$posXY = paste(offline$posX, offline$posY, sep = "-")

byLocAngleAP = with(offline, 
                    by(offline, list(posXY, angle, mac), 
                       function(x) x))

signalSummary = 
  lapply(byLocAngleAP,            
         function(oneLoc) {
           ans = oneLoc[1, ]
           ans$medSignal = median(oneLoc$signal)
           ans$avgSignal = mean(oneLoc$signal)
           ans$num = length(oneLoc$signal)
           ans$sdSignal = sd(oneLoc$signal)
           ans$iqrSignal = IQR(oneLoc$signal)
           ans
           })

offlineSummary = do.call("rbind", signalSummary)
```

Box diagram of standard deviation with interval average signal strength

```{r}
breaks = seq(-90, -30, by = 5)
```

The smooth scatter plot and the loess estimate of the difference between the mean and median of the signal strength versus the number of observations

```{r}
with(offlineSummary,
     smoothScatter((avgSignal - medSignal) ~ num,
                   xlab = "Number of Observations", 
                   ylab = "mean - median"))
abline(h = 0, col = "#984ea3", lwd = 2)

lo.obj = 
  with(offlineSummary,
       loess(diff ~ num, 
             data = data.frame(diff = (avgSignal - medSignal),
                               num = num)))

lo.obj.pr = predict(lo.obj, newdata = data.frame(num = (70:120)))
lines(x = 70:120, y = lo.obj.pr, col = "#4daf4a", lwd = 2)
```
Figure 3

```{r}
surfaceSS = function(data, mac, angle = 45) {
  require(fields)
  oneAPAngle = data[ data$mac == mac & data$angle == angle, ]
  smoothSS = Tps(oneAPAngle[, c("posX","posY")], 
                 oneAPAngle$avgSignal)
  vizSmooth = predictSurface(smoothSS)
  plot.surface(vizSmooth, type = "C", 
               xlab = "", ylab = "", xaxt = "n", yaxt = "n")
  points(oneAPAngle$posX, oneAPAngle$posY, pch=19, cex = 0.5) 
}

```

Estimation of signal strength for two access points and directions of 0 and 135 degrees

```{r}
parCur = par(mfrow = c(2,2), mar = rep(1, 4))

mapply(surfaceSS, mac = subMacs[ rep(c(5, 1), each = 2) ], 
       angle = rep(c(0, 135), 2),
       data = list(data = offlineSummary))
```
Figure 4


```{r}
par(parCur)
```

Distance calculation using 6 Access Points

```{r}
offlineSummary = subset(offlineSummary, mac != subMacs[2])

AP = matrix( c( 7.5, 6.3, 2.5, -.8, 12.8, -2.8,  
                1, 14, 33.5, 9.3,  33.5, 2.8),
            ncol = 2, byrow = TRUE,
            dimnames = list(subMacs[ -2 ], c("x", "y") ))
AP
```

```{r}
diffs = offlineSummary[ , c("posX", "posY")] - 
          AP[ offlineSummary$mac, ]

offlineSummary$dist = sqrt(diffs[ , 1]^2 + diffs[ , 2]^2)
```


## Method


### Simple Average Vs Weighted Average

Function to read online data
```{r}
macs = unique(offlineSummary$mac)

#Changede from 'Data/offline.final.trace.txt'
readData = 
  function(filename = 'http://www.rdatasciencecases.org/Data/offline.final.trace.txt', 
           subMacs = c("00:0f:a3:39:e1:c0", "00:0f:a3:39:dd:cd", "00:14:bf:b1:97:8a",
                       "00:14:bf:3b:c7:c6", "00:14:bf:b1:97:90", "00:14:bf:b1:97:8d",
                       "00:14:bf:b1:97:81"))
  {
    txt = readLines(filename)
    lines = txt[ substr(txt, 1, 1) != "#" ]
    tmp = lapply(lines, processLine)
    offline = as.data.frame(do.call("rbind", tmp), 
                            stringsAsFactors= FALSE) 
    
    names(offline) = c("time", "scanMac", 
                       "posX", "posY", "posZ", "orientation", 
                       "mac", "signal", "channel", "type")
    
     # keep only signals from access points
    offline = offline[ offline$type == "3", ]
    
    # drop scanMac, posZ, channel, and type - no info in them
    dropVars = c("scanMac", "posZ", "channel", "type")
    offline = offline[ , !( names(offline) %in% dropVars ) ]
    
    # drop more unwanted access points
    offline = offline[ offline$mac %in% subMacs, ]
    
    # convert numeric values
    numVars = c("time", "posX", "posY", "orientation", "signal")
    offline[ numVars ] = lapply(offline[ numVars ], as.numeric)

    # convert time to POSIX
    offline$rawTime = offline$time
    offline$time = offline$time/1000
    class(offline$time) = c("POSIXt", "POSIXct")
    
    # round orientations to nearest 45
    offline$angle = roundOrientation(offline$orientation)
      
    return(offline)
  }


online = readData("http://www.rdatasciencecases.org/Data/online.final.trace.txt", subMacs = macs)

online$posXY = paste(online$posX, online$posY, sep = "-")

length(unique(online$posXY))

```

Tally the number of signal strenghts recoreded at each location
```{r}
tabonlineXYA = table(online$posXY, online$angle)
tabonlineXYA[1:6, ]
```

Summarizing the online data and organizing the data to have 6 columns of signal strengths
```{r}
keepVars = c("posXY", "posX","posY", "orientation", "angle")
byLoc = with(online, 
             by(online, list(posXY), 
                function(x) {
                  ans = x[1, keepVars]
                  avgSS = tapply(x$signal, x$mac, mean)
                  y = matrix(avgSS, nrow = 1, ncol = 6,
                        dimnames = list(ans$posXY, names(avgSS)))
                  cbind(ans, y)
                }))

onlineSummary = do.call("rbind", byLoc)  

dim(onlineSummary)

```

```{r}

#Remove?
#names(onlineSummary)
```

Aggregating Signal Strength
```{r}
#Function for 6 MAC Addresses
reshapeSS = function(data, varSignal = "signal", 
                     keepVars = c("posXY", "posX","posY"),
                     sampleAngle = FALSE, 
                     refs = seq(0, 315, by = 45)) {
  byLocation =
    with(data, by(data, list(posXY), 
                  function(x) {
                    if (sampleAngle) {
                      x = x[x$angle == sample(refs, size = 1), ]}
                    ans = x[1, keepVars]
                    avgSS = tapply(x[ , varSignal ], x$mac, mean)
                    y = matrix(avgSS, nrow = 1, ncol = 6,
                               dimnames = list(ans$posXY,
                                               names(avgSS)))
                    cbind(ans, y)
                  }))

  newDataSS = do.call("rbind", byLocation)
  return(newDataSS)
}
```

```{r}
#Function for 7 MAC Addressess
reshapeSS_2 = function(data, varSignal = "signal", 
                     keepVars = c("posXY", "posX","posY"),
                     sampleAngle = FALSE, 
                     refs = seq(0, 315, by = 45)) {
  byLocation =
    with(data, by(data, list(posXY), 
                  function(x) {
                    if (sampleAngle) {
                      x = x[x$angle == sample(refs, size = 1), ]}
                    ans = x[1, keepVars]
                    avgSS = tapply(x[ , varSignal ], x$mac, mean)
                    y = matrix(avgSS, nrow = 1, ncol = 7,
                               dimnames = list(ans$posXY,
                                               names(avgSS)))
                    cbind(ans, y)
                  }))

  newDataSS = do.call("rbind", byLocation)
  return(newDataSS)
}
```


```{r}
selectTrain = function(angleNewObs, signals = NULL, m = 1){
  # m is the number of angles to keep between 1 and 5
  refs = seq(0, by = 45, length  = 8)
  nearestAngle = roundOrientation(angleNewObs)
  
  if (m %% 2 == 1) 
    angles = seq(-45 * (m - 1) /2, 45 * (m - 1) /2, length = m)
  else {
    m = m + 1
    angles = seq(-45 * (m - 1) /2, 45 * (m - 1) /2, length = m)
    if (sign(angleNewObs - nearestAngle) > -1) 
      angles = angles[ -1 ]
    else 
      angles = angles[ -m ]
  }
  angles = angles + nearestAngle
  angles[angles < 0] = angles[ angles < 0 ] + 360
  angles[angles > 360] = angles[ angles > 360 ] - 360
  angles = sort(angles) 
  
  offlineSubset = signals[ signals$angle %in% angles, ]
  reshapeSS(offlineSubset, varSignal = "avgSignal")
}

```

Training data when m = 3 and 130 degrees

```{r}
train130 = selectTrain(130, offlineSummary, m = 3)
head(train130)
```

```{r}
length(train130[[1]])
```

A functions of extracting training data 

```{r}
# Simple average
findNN = function(newSignal, trainSubset) {
  diffs = apply(trainSubset[ , 4:9], 1, 
                function(x) x - newSignal)
  dists = apply(diffs, 2, function(x) sqrt(sum(x^2)) )
  closest = order(dists)
  return(trainSubset[closest, 1:3 ])
}

#Weighted avearge
findNN_2 = function(newSignal, trainSubset) {
  diffs = apply(trainSubset[ , 4:9], 1, 
                function(x) x - newSignal)
  dists = apply(diffs, 2, function(x) sqrt(sum(x^2)) )
  closest = order(dists)
  wdists= trainSubset[closest, 1:3]
  wdists$dist = dists[closest]
  wdists$wt = 1/wdists$dist
  return(wdists)
}
```


Function predicted by k-NN

```{r}
#Simple Average
predXY = function(newSignals, newAngles, trainData, 
                  numAngles = 1, k = 3){
  
  closeXY = list(length = nrow(newSignals))
  
  for (i in 1:nrow(newSignals)) {
    trainSS = selectTrain(newAngles[i], trainData, m = numAngles)
    closeXY[[i]] = 
      findNN(newSignal = as.numeric(newSignals[i, ]), trainSS)
  }

  estXY = lapply(closeXY, 
                 function(x) sapply(x[ , 2:3], 
                                    function(x) mean(x[1:k])))
  estXY = do.call("rbind", estXY)
  return(estXY)
}

#Weighted Average
predXY_2 = function(newSignals, newAngles, trainData, 
                  numAngles = 1, k = 3){
  
  closeXY = list(length = nrow(newSignals))
  
  for (i in 1:nrow(newSignals)) {
    trainSS = selectTrain(newAngles[i], trainData, m = numAngles)
    closeXY[[i]] = 
      findNN_2(newSignal = as.numeric(newSignals[i, ]), trainSS)
  }

  estXY = lapply(closeXY, function(a) sapply(a[,2:3], function(b) weighted.mean(b[1:k],a[1:k,5])))
  estXY = do.call("rbind", estXY)
  return(estXY)
}

```

Test for 3-way, 3-NN, 1-NN

```{r}
estXYk3 = predXY(newSignals = onlineSummary[ , 6:11], 
                 newAngles = onlineSummary[ , 4], 
                 offlineSummary, numAngles = 3, k = 3)

estXYk3a = predXY_2(newSignals = onlineSummary[ , 6:11], 
                 newAngles = onlineSummary[ , 4], 
                 offlineSummary, numAngles = 3, k = 3)

estXYk1 = predXY(newSignals = onlineSummary[ , 6:11], 
                 newAngles = onlineSummary[ , 4], 
                 offlineSummary, numAngles = 3, k = 1)
```

floorErrorMap function: Example of a red line between the test position (.) and the predicted position (*) and the example. 1-NN (below) looks better than 3-NN

```{r}
floorErrorMap = function(estXY, actualXY, trainPoints = NULL, AP = NULL){
  
    plot(0, 0, xlim = c(0, 35), ylim = c(-3, 15), type = "n",
         xlab = "", ylab = "", axes = FALSE)
    box()
    if ( !is.null(AP) ) points(AP, pch = 15)
    if ( !is.null(trainPoints) )
      points(trainPoints, pch = 19, col="grey", cex = 0.6)
    
    points(x = actualXY[, 1], y = actualXY[, 2], 
           pch = 19, cex = 0.8 )
    points(x = estXY[, 1], y = estXY[, 2], 
           pch = 8, cex = 0.8 )
    segments(x0 = estXY[, 1], y0 = estXY[, 2],
             x1 = actualXY[, 1], y1 = actualXY[ , 2],
             lwd = 2, col = "red")
}

trainPoints = offlineSummary[ offlineSummary$angle == 0 & 
                              offlineSummary$mac == "00:0f:a3:39:e1:c0" ,
                        c("posX", "posY")]

floorErrorMap(estXYk3, onlineSummary[ , c("posX","posY")], 
              trainPoints = trainPoints, AP = AP)
```

```{r}
floorErrorMap(estXYk1, onlineSummary[ , c("posX","posY")], 
              trainPoints = trainPoints, AP = AP)
```



```{r}
calcError = 
function(estXY, actualXY) 
   sum( rowSums( (estXY - actualXY)^2) )

actualXY = onlineSummary[ , c("posX", "posY")]
sapply(list(estXYk1, estXYk3), calcError, actualXY)
```


Selection of k value
11-fold CV: 15 locations each

```{r}
v = 11
permuteLocs = sample(unique(offlineSummary$posXY))
permuteLocs = matrix(permuteLocs, ncol = v, 
                     nrow = floor(length(permuteLocs)/v))
```

```{r}
onlineFold = subset(offlineSummary, posXY %in% permuteLocs[ , 1])

reshapeSS = function(data, varSignal = "signal", 
                     keepVars = c("posXY", "posX","posY"),
                     sampleAngle = FALSE, 
                     refs = seq(0, 315, by = 45)) {
  byLocation =
    with(data, by(data, list(posXY), 
                  function(x) {
                    if (sampleAngle) {
                      x = x[x$angle == sample(refs, size = 1), ]}
                    ans = x[1, keepVars]
                    avgSS = tapply(x[ , varSignal ], x$mac, mean)
                    y = matrix(avgSS, nrow = 1, ncol = 6,
                               dimnames = list(ans$posXY,
                                               names(avgSS)))
                    cbind(ans, y)
                  }))

  newDataSS = do.call("rbind", byLocation)
  return(newDataSS)
}

offline = offline[ offline$mac != "00:0f:a3:39:dd:cd", ]

keepVars = c("posXY", "posX","posY", "orientation", "angle")

onlineCVSummary = reshapeSS(offline, keepVars = keepVars, 
                            sampleAngle = TRUE)

onlineFold = subset(onlineCVSummary, 
                    posXY %in% permuteLocs[ , 1])

offlineFold = subset(offlineSummary,
                     posXY %in% permuteLocs[ , -1])

estFold = predXY(newSignals = onlineFold[ , 6:11], 
                 newAngles = onlineFold[ , 4], 
                 offlineFold, numAngles = 3, k = 3)

estFold2 = predXY_2(newSignals = onlineFold[ , 6:11], 
                 newAngles = onlineFold[ , 4], 
                 offlineFold, numAngles = 3, k = 3)

actualFold = onlineFold[ , c("posX", "posY")]
calcError(estFold, actualFold)
calcError(estFold2, actualFold)

```



### Removing MAC Addresses

```{r}
allMacs = c("00:0f:a3:39:dd:cd", "00:0f:a3:39:e1:c0",
 "00:14:bf:3b:c7:c6", "00:14:bf:b1:97:81",
 "00:14:bf:b1:97:8a", "00:14:bf:b1:97:8d", "00:14:bf:b1:97:90")

keepVars = c("posXY", "posX", "posY", "orientation", "angle")
```

##### Removing 00:0f:a3:39:dd:cd

```{r}
macs_text = allMacs[2:7] # as in the text, without access point DD:CD
offline = readData(subMacs=macs_text)
online = readData("http://www.rdatasciencecases.org/Data/online.final.trace.txt", subMacs=macs_text)

#adding Code here
offline$posXY = paste(offline$posX, offline$posY, sep = "-")


# Create a list of data frames for every combination of (x,y), angle, and access point
byLocAngleAP = with(offline, by(offline, list(posXY, angle, mac), function(x) x))

# Calculate summary statistics on each of these data frames
signalSummary = lapply(byLocAngleAP,
 function(oneLoc) {
 ans = oneLoc[1, ]
ans$medSignal = median(oneLoc$signal)
ans$avgSignal = mean(oneLoc$signal)
ans$num = length(oneLoc$signal)
ans$sdSignal = sd(oneLoc$signal)
ans$iqrSignal = IQR(oneLoc$signal)
ans
 })

offlineSummary = do.call("rbind", signalSummary)
online$posXY = paste(online$posX, online$posY, sep = "-")
byLoc = with(online,
 by(online, list(posXY),
 function(x) {
 ans = x[1, keepVars]
 avgSS = tapply(x$signal, x$mac, mean)
 y = matrix(avgSS, nrow=1, ncol=6, dimnames=list(ans$posXY, names(avgSS)))
 cbind(ans, y)
 }))
onlineSummary = do.call("rbind", byLoc)
v = 11
permuteLocs = sample(unique(offlineSummary$posXY))
permuteLocs = matrix(permuteLocs, ncol=v, nrow=floor(length(permuteLocs)/v))
onlineCVSummary = reshapeSS(offline, keepVars=keepVars, sampleAngle=TRUE)
# Try K-nearest neighbors prediction for values of k from 1 to 20
K = 20
err = rep(0, K)
for (j in 1:v)
{
 onlineFold = subset(onlineCVSummary, posXY %in% permuteLocs[,j])
 offlineFold = subset(offlineSummary, posXY %in% permuteLocs[,-j])
 actualFold = onlineFold[ , c("posX", "posY")]
 for ( k in 1:K )
 {
 estFold = predXY(newSignals = onlineFold[,6:11], newAngles=onlineFold[,4], offlineFold,
numAngles=3, k=k)
 thisError = calcError(estFold, actualFold)
 err[k] = err[k] + thisError
 }
}


plot(y = err, x = (1:K),  type = "l", lwd= 2,
     #ylim = c(1200, 2100),
     xlab = "Number of Neighbors",
     ylab = "Sum of Square Errors")
rmseMin = min(err)
kMin = which(err == rmseMin)[1]
segments(x0 = 0, x1 = kMin, y0 = rmseMin, col = gray(0.4), 
         lty = 2, lwd = 2)
segments(x0 = kMin, x1 = kMin, y0 = 1100,  y1 = rmseMin, 
         col = grey(0.4), lty = 2, lwd = 2)

#mtext(kMin, side = 1, line = 1, at = kMin, col = grey(0.4))
text(x = kMin - 2, y = rmseMin + 40, 
     label = as.character(round(rmseMin)), col = grey(0.4))




```

##### Remvoing 00:0f:a3:39:e1:c0

```{r}
macs_text2 = allMacs[c(1,3:7)] # as in the text, without access point DD:CD
offline = readData(subMacs=macs_text2)
online = readData("http://www.rdatasciencecases.org/Data/online.final.trace.txt", subMacs=macs_text2)

#adding Code here
offline$posXY = paste(offline$posX, offline$posY, sep = "-")


# Create a list of data frames for every combination of (x,y), angle, and access point
byLocAngleAP = with(offline, by(offline, list(posXY, angle, mac), function(x) x))

# Calculate summary statistics on each of these data frames
signalSummary = lapply(byLocAngleAP,
 function(oneLoc) {
 ans = oneLoc[1, ]
ans$medSignal = median(oneLoc$signal)
ans$avgSignal = mean(oneLoc$signal)
ans$num = length(oneLoc$signal)
ans$sdSignal = sd(oneLoc$signal)
ans$iqrSignal = IQR(oneLoc$signal)
ans
 })

offlineSummary = do.call("rbind", signalSummary)
online$posXY = paste(online$posX, online$posY, sep = "-")
byLoc = with(online,
 by(online, list(posXY),
 function(x) {
 ans = x[1, keepVars]
 avgSS = tapply(x$signal, x$mac, mean)
 y = matrix(avgSS, nrow=1, ncol=6, dimnames=list(ans$posXY, names(avgSS)))
 cbind(ans, y)
 }))
onlineSummary = do.call("rbind", byLoc)
v = 11
permuteLocs = sample(unique(offlineSummary$posXY))
permuteLocs = matrix(permuteLocs, ncol=v, nrow=floor(length(permuteLocs)/v))
onlineCVSummary = reshapeSS(offline, keepVars=keepVars, sampleAngle=TRUE)
# Try K-nearest neighbors prediction for values of k from 1 to 20
K = 20
err = rep(0, K)
for (j in 1:v)
{
 onlineFold = subset(onlineCVSummary, posXY %in% permuteLocs[,j])
 offlineFold = subset(offlineSummary, posXY %in% permuteLocs[,-j])
 actualFold = onlineFold[ , c("posX", "posY")]
 for ( k in 1:K )
 {
 estFold = predXY(newSignals = onlineFold[,6:11], newAngles=onlineFold[,4], offlineFold,
numAngles=3, k=k)
 thisError = calcError(estFold, actualFold)
 err[k] = err[k] + thisError
 }
}
# Put err in a doggie bag for later
err.txt = err

plot(y = err, x = (1:K),  type = "l", lwd= 2,
     #ylim = c(1200, 2100),
     xlab = "Number of Neighbors",
     ylab = "Sum of Square Errors")
rmseMin = min(err)
kMin = which(err == rmseMin)[1]
segments(x0 = 0, x1 = kMin, y0 = rmseMin, col = gray(0.4), 
         lty = 2, lwd = 2)
segments(x0 = kMin, x1 = kMin, y0 = 1100,  y1 = rmseMin, 
         col = grey(0.4), lty = 2, lwd = 2)

#mtext(kMin, side = 1, line = 1, at = kMin, col = grey(0.4))
text(x = kMin - 2, y = rmseMin + 40, 
     label = as.character(round(rmseMin)), col = grey(0.4))


```



## Conclusion

In conclusion, After removing MAC Address 00:0f:a3:39:e1:c0 and adding 00:0f:a3:39:dd:cd, then keeping both MAC addresses in it appears that the correct MAC address that should have been removed was 00:0f:a3:39:dd:cd. Removing 00:0f:a3:39:dd:cd was the step used in the original case study and after further analysis seems to be that 00:0f:a3:39:dd:cd should not be used in RTLS and 00:0f:a3:39:e1:c0 should be used in RTLS. 00:0f:a3:39:e1:c0 yields the best prediction for location between the two MAC addresses. Using data for both MAC addresses simultaneously yield a less accurate prediction of location.

Also, after using an alternative approach to determining location where the weight is inversely proportional to distance from the test observations it seems as if the  weighted average is slightly better method when comparing to the simple average outcome. 


## References

Nolan, D., & Lang, D. T. (2015). Data Science in R: A Case Studies Approach to Computational Reasoning and Problem Solving. Chapman and Hall/CRC; 1 edition.